Cybersickness remains a barrier to virtual reality (VR) adoption, and subjective questionnaires alone are insufficient for system-level diagnosis of its determinants.
This systematic review, conducted following the PRISMA 2020 statement, examines neuromarkers of cybersickness in VR: signals derived from non-invasive recording or modulation of brain activity that index or modulate the user's state.
A search of PubMed, Web of Science, and Scopus up to 27 March 2025 identified 92 eligible studies: 77 using electroencephalography, 4 using functional near-infrared spectroscopy, and 11 using neurostimulation (5 galvanic vestibular stimulation, 3 transcranial direct-current stimulation, 2 transcranial alternating-current stimulation, 1 other). No eligible studies using fMRI, MEG, or PET were retrieved.
Across electroencephalography studies, cybersickness is associated with increased low-frequency power (delta, theta) and decreased alpha-band power, with topographies varying by paradigm and hardware.
At the corpus level, VR display hardware significantly modulates band-power responses (alpha: $p=0.0036$, large effect; beta: $p=0.0146$), indicating that prior contradictions in the literature are partly attributable to hardware confounds rather than to differences in cybersickness per se.
A methodological audit of the 38 classification or prediction studies finds that only one reports leave-one-subject-out validation, nineteen do not disclose a sick-versus-non-sick decision threshold, and thirteen report accuracy without sensitivity, specificity, AUC, or F1.
Relative to the most recent prior scoping review \cite{changBrainActivityCybersickness2023}, which covered 33 EEG-only studies up to September 2021, this review covers a larger and more recent corpus, explicitly includes neurostimulation alongside neuroimaging, and contributes corpus-level meta-analytic findings.
We outline reporting recommendations and identify closed-loop modulation and individual susceptibility prediction as directions where the existing corpus already provides actionable starting points.
