The adverse effects of cybersickness remain a significant obstacle to the widespread adoption and prolonged use of Virtual Reality.
Brain-Computer Interfaces have emerged as a promising approach for moving beyond subjective reports toward more objective measurement, prediction, and potential mitigation of this debilitating condition.
This paper has provided a systematic and critical review of the literature at the intersection of BCI and cybersickness, synthesizing the current state of knowledge and identifying key challenges and opportunities.

Our synthesis suggests an emerging neurophysiological signature of cybersickness, primarily characterized by increased low-frequency (delta, theta) power and a suppression of alpha-band oscillations in the EEG.
Spatially precise modalities like fMRI and fNIRS have localized these dynamics to a network of brain regions including the insula, cingulate cortex, and areas involved in visual-vestibular processing.
This foundational knowledge has facilitated the development of computational models, many based on deep learning, that show promise in classifying sickness states, though accuracy claims require careful interpretation given methodological limitations.
This research has led to the development of early-stage, real-time, closed-loop adaptive systems that attempt to use neural feedback to modify the VR environment and potentially reduce user discomfort.

However, this review also highlights that the field is hampered by significant methodological heterogeneity, a lack of standardized protocols and ground-truth labels, and a frequent reliance on small, demographically-limited samples.
These challenges severely limit the generalizability and replicability of many findings and impede the direct comparison of results across studies.
The path toward robust, generalizable BCI applications for cybersickness management requires a concerted shift toward open science practices, including the development of benchmark datasets and standardized evaluation metrics.
It also necessitates a move from purely correlational findings to causal investigations and the validation of systems in ecologically relevant, real-world contexts.

In conclusion, the integration of BCI with VR represents more than a novel tool for studying cybersickness; it is a critical enabling technology for the future of immersive computing.
The development of truly user-aware systems that can implicitly monitor and dynamically adapt to a user's neurophysiological state in real-time may help address one of the most persistent barriers to the widespread adoption of VR.
This line of research is essential for paving the way for experiences that are not only more immersive and effective, but also universally comfortable and accessible.